\begin{thebibliography}{99}

\bibitem{bib:ldd3}
  J. Corbet, A. Rubini i G. Kroah-Hartman,
  \emph{Linux Device Drivers, Third Edition}.
  2005.
  \url{http://lwn.net/Kernel/LDD3/}

\bibitem{bib:taocp-fa}
  Donald Knuth,
  \emph{The Art of Computer Programming. Volume 1: Fundamental
    Algorithms},
  Third Edition,
  Massachusetts, 1997.
  ISBN 0-201-89683-4

\bibitem{bib:v2.6.38}
  J. Corbet,
  \emph{Kernel release status},
  16 marca 2011.
  \url{http://lwn.net/Articles/433896/}

\bibitem{bib:compaction}
  J. Corbet,
  \emph{Memory compaction},
  6 stycznia 2010.
  \url{http://lwn.net/Articles/368869/}

\bibitem{bib:cma-and-arm}
  J. Corbet,
  \emph{CMA and ARM},
  5 czerwca 2011.
  \url{http://lwn.net/Articles/450286/}

\bibitem{patch:cma-24}
  M. Nazarewicz i~M. Szyprowski,
  \emph{Contiguous Memory Allocator, v.\ 24},
  3 kwietnia 2012.
  \url{http://thread.gmane.org/gmane.linux.kernel.mm/76241}

\bibitem{patch:pmm}
  M. Nazarwicz,
  \emph{Physical Memory Management}.
  13 maja 2009.
  \url{http://lkml.org/lkml/2009/5/13/100}

\bibitem{patch:cma-4}
  M. Nazarewicz,
  \emph{The Contiguous Memory Allocator framework, v.\ 4},
  20 sierpnia 2010.
  \url{http://thread.gmane.org/gmane.linux.kernel.mm/52010}

\bibitem{patch:bigphys}
  D. Tochansky,
  \emph{bigphysarea patch for 3.2.x},
  27 marca 2012.
  \url{http://article.gmane.org/gmane.linux.kernel/1273100}

\bibitem{patch:cma-test}
  Barry Song,
  \emph{A simple kernel module as a helper to test CMA, v. 4},
  7 marca 2012.
  \url{http://thread.gmane.org/gmane.linux.kernel/1263136}

%% \bibitem{bib:state-of-allocators}
%%   D. Rientjes,
%%   \emph{Status of the Linux Slab Allocators}.
%%   Southern California Linux Expo, February 26, 2011
%%   \url{http://www.socallinuxexpo.org/scale9x/presentations/status-linux-slab-allocators.html}

\end{thebibliography}
