% Copyright (c) 2012 by Michał Nazarewicz <mina86@mina86.com>
% Distributed under the terms of the Creative Commons
% Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) license.

\subsection{Solutions to the problem}

\begin{frame}
  \frametitle{Lie to the kernel}

  \begin{itemize}
  \item Lie to the kernel about amount of memory.
    \begin{itemize}
    \item Easily done with a~\code{mem} parameter.
    \item Kernel won't touch memory hidden via \code{mem}.
    \end{itemize}
  \item Assign buffers to each device that might need it.
  \item Platform dependent.
  \item Requires fiddling with boot loader.
  \item \ldots
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Reserve and assign at boot time}

  \begin{itemize}
  \item Reserve memory during system boot time.
  \item Assign buffers to each device that might need it.
  \item Less platform dependent.
  \item Boot loader is left alone.
  \item While device is not being used, memory is wasted.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Reserve but allocate on demand}

  \begin{itemize}
  \item Reserve memory during system boot time.
  \item Provide API for allocating from that reserved pool.
  \item Less memory is reserved.
  \item But it's still wasted.
  \end{itemize}

  \begin{itemize}
  \item bigphysarea
  \item Physical Memory Manager
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Reserve but give back}

  \begin{itemize}
  \item Reserve memory during system boot time.
  \item Give it back
    \begin{itemize}
    \item but set it up so only movable pages can be allocated.
    \end{itemize}
  \item Provide API for allocating from that reserved pool.
  \item Migrate pages on allocation.
  \end{itemize}

  \begin{itemize}
  \item Contiguous Memory Allocator
  \end{itemize}
\end{frame}
