\subsection{Integration with the architecture}

\begin{frame}
  \frametitle{Integration with the architecture}

  \begin{itemize}
  \item CMA needs to be integrated with the architecture.
  \item Memory needs to be reserved.
  \item There are early fixups to be done. {\footnotesize Or not.}
  \item The DMA API needs to be made aware of CMA.
  \item And Kconfig needs to be instructed to allow CMA.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Memory reservation}

  \begin{itemize}
  \item \code{memblock} must be ready, page allocator must not.
  \item On ARM, \code{arm_memblock_init()} is a~good place.
  \item All one needs to do, is call
    \code{dma_contiguous_reserve()}.
  \end{itemize}

  \begin{block}{Memory reservation}
\begin{lstlisting}
void __init dma_contiguous_reserve(
    phys_addr_t limit);
\end{lstlisting}
  \end{block}

  \begin{description}[limitAA]
  \item[{\ttfamily limit}] Upper limit of the region (or zero for no
    limit).
  \end{description}

\end{frame}

\begin{frame}[fragile]
  \frametitle{Memory reservation, cont.}

  \begin{block}{Reserving memory on ARM}
\begin{lstlisting}[language=diff]
 if (mdesc->reserve)
     mdesc->reserve();

+/*
+ * reserve memory for DMA contigouos allocations,
+ * must come from DMA area inside low memory
+ */
+dma_contiguous_reserve(min(arm_dma_limit, arm_lowmem_limit));
+
 arm_memblock_steal_permitted = false;
 memblock_allow_resize();
 memblock_dump_all();
\end{lstlisting}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Early fixups}

  \begin{itemize}
  \item Kernel linear mapping uses huge pages.
  \item On ARM cache is not coherent.
  \item Having two mappings with different cache-ability gives
    undefined behaviour.
  \item So on ARM an “early fixup” is needed.
    \begin{itemize}
    \item This fixup alters the linear mapping so CMA regions use
      \unit[4]{KiB} pages.
    \end{itemize}
  \item The fixup is defined in
    \code{dma_contiguous_early_fixup()} function
    \begin{itemize}
    \item which architecture needs to provide
    \item with declaration in a~\code{asm/dma-contiguous.h} header file.
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Early fixups, cont.}

  \begin{block}{No need for early fixups}
\begin{lstlisting}
#ifndef ASM_DMA_CONTIGUOUS_H
#define ASM_DMA_CONTIGUOUS_H

#ifdef __KERNEL__

#include <linux/types.h>
#include <asm-generic/dma-contiguous.h>

static inline void
dma_contiguous_early_fixup(phys_addr_t base, unsigned long size)
{ /* nop, no need for early fixups */ }

#endif
#endif
\end{lstlisting}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Integration with DMA API}

  \begin{itemize}
  \item The DMA API needs to be modified to use CMA.
  \item CMA most likely won't be the only one.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Integration with DMA API}

  \begin{block}{Allocate}
\begin{lstlisting}
struct page *dma_alloc_from_contiguous(
    struct device *dev,
    int count,
    unsigned int align);
\end{lstlisting}
  \end{block}

  \begin{description}[countAA]
  \item[{\ttfamily dev}] Device the allocation is performed on behalf
    of.
  \item[{\ttfamily count}] \emph{Number of pages} to
    allocate. {\footnotesize Not number of bytes nor order.}
  \item[{\ttfamily align}] Order which to align to.  Limited by
    Kconfig option.
  \item Returns page that is the first page of \code{count} allocated
    pages. {\footnotesize It's not a~compound page.}
  \end{description}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Integration with DMA API}

  \begin{block}{Release}
\begin{lstlisting}
bool dma_release_from_contiguous(
    struct device *dev,
    struct page *pages,
    int count);
\end{lstlisting}
  \end{block}

  \begin{description}[countAA]
  \item[{\ttfamily dev}] Device the allocation was performed on behalf
    of.
  \item[{\ttfamily pages}] The first of allocated
    pages. {\footnotesize As returned on allocation.}
  \item[{\ttfamily count}] Number of allocated pages.
  \item Returns \code{true} if memory was freed (ie.\ was managed by
    CMA) or \code{false} otherwise.
  \end{description}
\end{frame}

\begin{frame}
  \frametitle{Let it compile!}

  \begin{itemize}
  \item There's one think that needs to be done in \code{Kconfig}.
  \item Architecture needs to \code{select HAVE_DMA_CONTIGUOUS}.
  \item Without it, CMA won't show up under “Generic Driver Options”.
  \item Architecture may also \code{select CMA} to force CMA in.
  \end{itemize}
\end{frame}
